Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-03-18 doc/manuscript/ESSDmanuscript.tex
knit on my laptop
@mawilliams99 , this is great that you got it to knit! I noticed that the tables at the end didn't knit properly, though. I have no idea what's going on, but pushing my version for you to see the difference

@@

@@

@@

\conclusions[Conclusions]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\clearpage 
\section{Instructions (TEMPORARY)}

Regarding figures and tables in appendices, the following two options
are possible depending on your general handling of figures and tables in
the manuscript environment:

\subsection{Option 1}

If you sorted all figures and tables into the sections of the text,
please also sort the appendix figures and appendix tables into the
respective appendix sections. They will be correctly named
automatically.

\subsection{Option 2}

If you put all figures after the reference list, please insert appendix
tables and figures after the normal tables and figures.

To rename them correctly to A1, A2, etc., please add the following
commands in front of them: \texttt{\textbackslash{}appendixfigures}
needs to be added in front of appendix figures
\texttt{\textbackslash{}appendixtables} needs to be added in front of
appendix tables

Please add \texttt{\textbackslash{}clearpage} between each table and/or
figure. Further guidelines on figures and tables can be found below.

@@

CURRENT TABLE 2 GOES HERE
\noappendix

>>>>

ForC data is incredibly valuable to EFDB and there is data which is
included in the ForC database that does not meet EFDB standards. There
were two main EFDB guidelines which limits the amount of data we could
transfer. EFDB will not accept data which has been digitized(from graph)
and ForC does.

\section{Conclusions}

@@

\section{Appendix A}

@@

\section{Appendix B}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Mapping ForC to EFDB}

@@

CURRENT TABLE 3 GOES HERE
\noappendix
